H0LiCOW: correlation between black hole mass and host galaxy luminosity.

### 2020-02-25 manuscript/manuscript.tex
Create the table generator

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{subfig} %for figure subplot

@@

\section{Sample Selection}
We adopt the eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information for the information of these eight systems are given in Table~1 therein. Besides, half of the systems, including HE0435, RXJ1131, WFI2033 and HE1104 have \hst\ imaging data in multi-bands. To estimate the \mbh, we adopt the spectra information as inferred by \citet{Sluse2012, Peng2006, Shen2011}. We use a Table[] to summarize the data information. \ding{table should include the redshift, filter/Camera, the drizzled pixel size.}

@@

@@

Note that the residual maps are appears to be less ideal than the ones as presented by Ken[]. The major reason is the definition of the host galaxy. We compare the result with the inferred host galaxy by Ken[] and Ding+2017.

@@

>>>>

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{subfig} %for figure subplot
\usepackage{graphicx}
\usepackage[flushleft]{threeparttable}
\usepackage{xspace}

@@

\section{Sample Selection}
We adopt the eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information for the information of these eight systems are given in Table~1 therein. Besides, half of the systems, including HE0435, RXJ1131, WFI2033 and HE1104 have \hst\ imaging data in multi-bands. To estimate the \mbh, we adopt the spectra information as inferred by \citet{Sluse2012, Peng2006, Shen2011}. We use a Table[] to summarize the data information.

@@

\begin{table}
\centering
\caption{Summary of lensed AGN information.}\label{data_set}
%\resizebox{18cm}{!}{
     \begin{tabular}{ccccc}
        \hline
Object ID & camera & Filter & exposure & pixel scale \\
 & & & time (s) & (drizzled) \\ \hline
HE0435$-$1223 & WFC3-IR & F160W & 9340 & $0\farcs{}08$ \\
RXJ1131$-$1231 & ACS & F814W & 1980 & $0\farcs{}05$ \\
WFI2033$-$4723 & WFC3-IR & F160W & 26257 & $0\farcs{}08$ \\
SDSS1206$+$4332 & WFC3-IR & F160W & 8457 & $0\farcs{}08$ \\
HE1104$-$1805 & WFC3-IR & F160W & 14698 & $0\farcs{}08$ \\
SDSS0246$-$0825 & WFC3-UVIS & F814W & 8481 & $0\farcs{}03$ \\
HS2209$+$1914 & WFC3-UVIS & F814W & 14238 & $0\farcs{}03$ \\
HE0047$-$1756 & WFC3-UVIS & F814W & 9712 & $0\farcs{}03$ \\
        \hline
     \end{tabular}
    %}
    \begin{tablenotes}
      \small
      \item Note - To be written.
    \end{tablenotes} 
\end{table}

@@

Note that the residual level reveals in the inference figures are appears to be larger than the ones as presented by Ken[]. The major reason is the definition of the host galaxy in the models. Without using sophisticated models such as shepelet or pixellized ones, we will be able to infer directly the \sersic\ flux of the host galaxy.

We compare the result with the inferred host galaxy by Ken[] and Ding+2017.

@@

\begin{table*}
\centering
%\resizebox{12cm}{!}{
     \begin{tabular}{ccccccc}
\hline
Object ID & Magnitude & Host-Total Flux Ratio & Reff & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
 & (AB system) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
HE0435 & $21.332\substack{+0.208\\-0.175}$ & $62.471\pm10.893$ & $0.298\pm0.027$ & $2.829\pm0.251$ & $1.500$ & $10.978$ \\
RXJ1131$_{\rm bulge}$ & $22.074\substack{+0.164\\-0.142}$ & $91.573\pm11.280$ & $0.106\pm0.007$ & fix to 4 & $3.000$ & $10.276$ \\
RXJ1131$_{\rm disk}$ & $19.305\substack{+0.154\\-0.135}$ & $91.573\pm11.280$ & $0.875\pm0.062$ & fix to 1 & $1.500$ & $11.091$ \\
WFI2033 & $21.404\substack{+0.167\\-0.145}$ & $35.723\pm5.093$ & $0.294\pm0.025$ & $0.528\pm0.011$ & $0.625$ & $10.662$ \\
SDSS1206 & $21.287\substack{+0.222\\-0.184}$ & $32.286\pm5.977$ & $0.110\pm0.020$ & $4.526\pm0.555$ & $0.625$ & $10.781$ \\
HE1104 & $21.274\substack{+0.188\\-0.160}$ & $14.142\pm2.250$ & $0.265\pm0.026$ & $1.033\pm0.034$ & $0.625$ & $11.039$ \\
SDSS0246 & $23.575\substack{+0.394\\-0.289}$ & $3.756\pm1.143$ & $0.381\pm0.098$ & $4.963\pm0.048$ & $0.626$ & $10.690$ \\
HS2209 & $20.385\substack{+0.262\\-0.211}$ & $19.454\pm4.165$ & $1.921\pm1.070$ & $2.953\pm0.438$ & $1.001$ & $11.177$ \\
HE0047 & $22.972\substack{+0.626\\-0.394}$ & $2.496\pm1.093$ & $0.282\pm0.176$ & $3.603\pm1.533$ & $0.625$ & $10.888$ \\
\hline
\end{tabular}
    %}
\caption{Summary of lensed AGN inference.}\label{data_set}    
\small
\end{table*}
